Perturbed Gait Data

### 2014-10-18 paper.tex
Updated DFlowData pipeline description.

The \verb|motek.DFlowData| class stores all the data presented in the previous
section and encodes several ``cleaning'' operations to put the data into a
usable form.

\begin{itemize}
  \item Loads the meta data file into a Python dictionary.
  \item Loads the DFlow mocap module TSV file into Pandas \verb|DataFrame|.
  \item Relabels the column headers to more meaningful names if this is
    specified in the meta data.
  \item Identifies the missing values in the mocap marker data and replaces
    them with \verb|numpy.nan|.
  \item Interpolates the missing marker values and replaces them with
    interpolated estimates.
  \item Loads the DFlow record moudle TSV file into a Pandas \verb|DataFrame|.
  \item Extracts the events and creates a dictionary mapping the event names in
    the meta data to the events detected in the record module file.
  \item Merges the data from the mocap module and record module into one data
    frame at the maximum common constant sample rate.
  \item Extracts sections of the data bounded by the events.
  \item Saves the cleaned data to disk.
\end{itemize}

>>>>

The \verb|motek.DFlowData| class collects and stores all the raw data presented
in the previous section and applies several ``cleaning'' operations to put the
data into a usable form.

\begin{itemize}
  \item Loads the meta data file into a Python dictionary.
  \item Loads the DFlow mocap module TSV file into Pandas \verb|DataFrame|.
  \item Relabels the column headers to more meaningful names if this is
    specified in the meta data.
  \item Optionally identifies the missing values in the mocap marker data and
    replaces them with \verb|numpy.nan|.
  \item Optionally interpolates the missing marker values and replaces them
    with interpolated estimates using a variety of interpolation methods.
  \item Loads the D-Flow record moudle TSV file into a Pandas \verb|DataFrame|.
  \item Extracts the events and creates a dictionary mapping the event names in
    the meta data to the events detected in the record module file.
  \item Compensates the ground reaction loads for treadmill motion.
  \item Merges the data from the mocap module and record module into one data
    frame at the maximum common constant sample rate.
  \item Extracts sections of the data bounded by the events.
  \item Saves the cleaned data to disk.
\end{itemize}
